A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
rename chunks

Now remove any non-DMI treatments or controls
```{r}
PM_MB_dat <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "control" |
             fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")
```

@@

### Yield variance standardisation
```{r}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(
      vi = 
         case_when(
            Y_error_type == "stdev" ~ disease_error ^2,
            Y_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      spray_management = fct_relevel(spray_management,sort)
   )

@@

### Disease severity variance standardisation
```{r}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(
      d_vi = 
         case_when(
            D_error_type == "stdev" ~ disease_error ^2,
            D_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      id = row_number(),
      spray_management = fct_relevel(spray_management,sort)
   )

>>>>

Now remove any non-DMI treatments or controls
```{r KeepOnlyDMI}
PM_MB_dat <- 
   PM_MB_dat %>%
   filter(fungicide_ai == "control" |
             fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")
```

@@

### Yield variance standardisation
```{r StandardiseYieldVariance}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(
      vi = 
         case_when(
            Y_error_type == "stdev" ~ disease_error ^2,
            Y_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      spray_management = fct_relevel(spray_management,sort)
   )

@@

### Disease severity variance standardisation
```{r StandardiseSeverityVariance}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(
      d_vi = 
         case_when(
            D_error_type == "stdev" ~ disease_error ^2,
            D_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      id = row_number(),
      spray_management = fct_relevel(spray_management,sort)
   )
